\begin{thebibliography}{99}
\small
\setlength{\itemsep}{3pt}
\setlength{\parsep}{0pt}
\setlength{\parskip}{0pt}

% --- NHÓM KHẢO SÁT THỊ TRƯỜNG & SỨC KHỎE CỘNG ĐỒNG (Chương 1) ---
\bibitem{QAndMeVN}
Q\&Me Market Research (2025), \textit{Vietnamese exercise behaviors -- Survey on Sports and Exercise Habits in Vietnam}, \url{https://qandme.net/en/report/vietnamese-exercise-behaviors.html} (Ngày truy cập: 10/05/2026).

\bibitem{WHO_COVID19}
World Health Organization -- WHO (2023), \textit{Coronavirus disease (COVID-19) -- Overview and WHO guidance}, \url{https://www.who.int/emergencies/diseases/novel-coronavirus-2019} (Ngày truy cập: 10/05/2026).

\bibitem{WHO_PhysicalActivity}
World Health Organization -- WHO (2022), \textit{Physical activity -- Fact Sheet}, \url{https://www.who.int/news-room/fact-sheets/detail/physical-activity} (Ngày truy cập: 10/05/2026).

% --- NHÓM CÔNG NGHỆ CỐT LÕI (Chương 1) ---
\bibitem{ReactJSDocs}
Meta Platforms, Inc. (2024), \textit{React v18 Documentation -- The library for web and native user interfaces}, \url{https://react.dev/} (Ngày truy cập: 10/05/2026).

\bibitem{ViteDocs}
Vite Team (2024), \textit{Vite -- Next Generation Frontend Tooling}, \url{https://vite.dev/} (Ngày truy cập: 10/05/2026).

\bibitem{TailwindCSSDocs}
Tailwind Labs (2024), \textit{Tailwind CSS -- A utility-first CSS framework for rapidly building custom user interfaces}, \url{https://tailwindcss.com/docs} (Ngày truy cập: 10/05/2026).

\bibitem{NodeJSDocs}
OpenJS Foundation (2024), \textit{Node.js v20.x LTS Documentation}, \url{https://nodejs.org/docs/} (Ngày truy cập: 10/05/2026).

\bibitem{TypeScriptDocs}
Microsoft (2024), \textit{TypeScript Documentation -- Typed JavaScript at Any Scale}, \url{https://www.typescriptlang.org/docs/} (Ngày truy cập: 10/05/2026).

\bibitem{ExpressJSDocs}
Express.js Team (2024), \textit{Express - Fast, unopinionated, minimalist web framework for Node.js}, \url{https://expressjs.com/} (Ngày truy cập: 10/05/2026).

\bibitem{MongoDBDocs}
MongoDB, Inc. (2024), \textit{MongoDB Manual v7.0 -- The Document Database}, \url{https://www.mongodb.com/docs/} (Ngày truy cập: 10/05/2026).

\bibitem{SocketIODocs}
Socket.io Team (2024), \textit{Socket.io Documentation -- Real-time bidirectional event-based communication}, \url{https://socket.io/docs/v4/} (Ngày truy cập: 10/05/2026).

\bibitem{GroqDocs}
Groq Cloud (2024), \textit{Groq API Reference -- LPU Inference Engine for LLMs}, \url{https://console.groq.com/docs} (Ngày truy cập: 10/05/2026).

\bibitem{GeminiAPIDocs}
Google DeepMind (2024), \textit{Gemini API Developer Guide -- Build with Google's most capable AI models}, \url{https://ai.google.dev/docs} (Ngày truy cập: 10/05/2026).

\bibitem{HelmetJS}
Helmet Contributors (2024), \textit{Helmet -- Help secure Express.js apps with various HTTP headers}, \url{https://helmetjs.github.io/} (Ngày truy cập: 10/05/2026).

% --- NHÓM ỨNG DỤNG & WEBSITE THAM KHẢO (Chương 2) ---
\bibitem{StravaWebsite}
Strava, Inc. (2024), \textit{Strava -- The \#1 app for runners and cyclists}, \url{https://www.strava.com} (Ngày truy cập: 10/05/2026).

\bibitem{ImgStrava}
Strava Engineering Blog (2024), \textit{Strava -- Front-End Development Articles and Interface Screenshots}, Medium, \url{https://medium.com/strava-engineering/tagged/front-end-development} (Ngày truy cập: 10/05/2026).

\bibitem{MyFitnessPal}
MyFitnessPal, Inc. (2024), \textit{MyFitnessPal -- Calorie Counter, Nutrition and Diet Tracker}, \url{https://www.myfitnesspal.com} (Ngày truy cập: 10/05/2026).

\bibitem{ImgMyFitnessPal}
AppleToolbox Staff (2019), \textit{The 4 Best Food Tracker Apps for 2019 -- MyFitnessPal Interface}, AppleToolbox, \url{https://appletoolbox.com/the-4-best-food-tracker-apps-for-2019/} (Ngày truy cập: 10/05/2026).

\bibitem{NikeTrainingClub}
Nike, Inc. (2024), \textit{Nike Training Club -- Expert-backed workouts and nutrition advice}, \url{https://www.nike.com/ntc-app} (Ngày truy cập: 10/05/2026).

\bibitem{ImgNTC}
ResearchGate (2018), \textit{Screenshots of Nike Training Club app user interface showing the daily log history}, ResearchGate Figure Repository, \url{https://www.researchgate.net/figure/Screenshots-of-Nike-Training-Club-app-user-interface-showing-A-the-daily-log-history_fig3_319987781} (Ngày truy cập: 10/05/2026).

% --- NHÓM TÀI LIỆU KỸ THUẬT BỔ SUNG (Chương 4) ---
\bibitem{CloudinaryDocs}
Cloudinary Ltd. (2024), \textit{Cloudinary Documentation -- Image and Video Management APIs}, \url{https://cloudinary.com/documentation} (Ngày truy cập: 10/05/2026).

\bibitem{GoongMapsAPI}
Goong Team (2024), \textit{Goong Maps API -- Nền tảng bản đồ số Việt Nam}, \url{https://docs.goong.io/} (Ngày truy cập: 10/05/2026).

\bibitem{GoogleOAuth}
Google LLC (2024), \textit{Google Identity -- OAuth 2.0 for Server-side Web Apps}, Google Developers, \url{https://developers.google.com/identity/protocols/oauth2} (Ngày truy cập: 10/05/2026).

\bibitem{NodemailerDocs}
Nodemailer Team (2024), \textit{Nodemailer -- Send e-mails from Node.js}, \url{https://nodemailer.com/} (Ngày truy cập: 10/05/2026).

\bibitem{TanStackQuery}
TanStack (2024), \textit{TanStack Query v5 -- Powerful asynchronous state management for TS/JS}, \url{https://tanstack.com/query} (Ngày truy cập: 10/05/2026).

\bibitem{ReactRouterDocs}
Remix Software (2024), \textit{React Router v6 -- Declarative routing for React applications}, \url{https://reactrouter.com/en/main} (Ngày truy cập: 10/05/2026).

\bibitem{JWTSpec}
M. Jones, J. Bradley, N. Sakimura (2015), \textit{RFC 7519: JSON Web Token (JWT)}, Internet Engineering Task Force (IETF).

% --- NHÓM TÀI LIỆU KỸ THUẬT & KIẾN THỨC BỔ SUNG (Chương 5) ---
\bibitem{TensorFlowJS}
Google LLC (2024), \textit{TensorFlow.js -- Machine Learning for the Web}, \url{https://www.tensorflow.org/js} (Ngày truy cập: 10/05/2026).

\bibitem{FaceApiJS}
Vincent Mühler (2023), \textit{face-api.js -- Face detection and face recognition in the browser implemented on top of the tensorflow.js core}, GitHub Repository, \url{https://github.com/justadudewhohacks/face-api.js}.

\bibitem{Healthline_TDEE}
Healthline Media (2024), \textit{How to Calculate Your TDEE, BMI, and BMR: The Definitive Guide}, \url{https://www.healthline.com/} (Ngày truy cập: 10/05/2026).

\bibitem{CompendiumPhysicalActivities}
B. E. Ainsworth et al. (2011), ``2011 Compendium of Physical Activities: A second update of codes and MET values'', \textit{Medicine \& Science in Sports \& Exercise}, vol.~43, no.~8, pp.~1575--1581. \url{https://pacompendium.com/} (Ngày truy cập: 10/05/2026).

\bibitem{NASM_MET}
National Academy of Sports Medicine - NASM (2024), \textit{Metabolic Equivalent of Task (MET) and Caloric Expenditure}, \url{https://www.nasm.org/} (Ngày truy cập: 10/05/2026).

\bibitem{VercelDocs}
Vercel Inc. (2024), \textit{Vercel Documentation -- Develop, Preview, Ship}, \url{https://vercel.com/docs} (Ngày truy cập: 10/05/2026).

\bibitem{WikiVPS}
Wikipedia (2024), \textit{Virtual private server}, \url{https://en.wikipedia.org/wiki/Virtual_private_server} (Ngày truy cập: 10/05/2026).

\bibitem{PM2Docs}
Keymetrics (2024), \textit{PM2 -- Advanced Node.js process manager}, \url{https://pm2.keymetrics.io/} (Ngày truy cập: 10/05/2026).

\bibitem{MongoDBAtlas}
MongoDB, Inc. (2024), \textit{MongoDB Atlas -- Multi-cloud developer data platform}, \url{https://www.mongodb.com/atlas} (Ngày truy cập: 10/05/2026).

% --- NHÓM KIỂM THỬ (Chương 6) ---
\bibitem{TestingPyramid}
Kaizenko (2024), \textit{What is the Testing Pyramid?}, \url{https://www.kaizenko.com/what-is-the-testing-pyramid/} (Ngày truy cập: 10/05/2026).

\bibitem{PageSpeedInsights}
Google (2024), \textit{PageSpeed Insights}, \url{https://pagespeed.web.dev/} (Ngày truy cập: 10/05/2026).

\bibitem{LoaderIO}
SendGrid (2024), \textit{Loader.io -- Simple Cloud Load Testing}, \url{https://loader.io/} (Ngày truy cập: 10/05/2026).

\bibitem{KiotVietGym}
KiotViet (2024), \textit{Phần mềm quản lý phòng tập Gym, Fitness, Yoga chuyên nghiệp}, \url{https://www.kiotviet.vn/} (Ngày truy cập: 10/05/2026).

\end{thebibliography}
